\section{Research Questions}\label{sec:research-questions}

In order to support individuals exploring large unstructured text data, 
this thesis aims to provide computational means to facilitate the work with large unstructured text data.
In this work, different methods to derive semantic and visual information from unstructured text data are applied.
The techniques ought to be compared and evaluated.

% research questions (allgemein damit nützlich und speziell für die Aufgabe -> beantwortbar, Erkenntnis allg Interesse & Operationalisierbar: Experiment)
In the following, the research questions addressed are defined:
\begin{description}
    \item[How can exploration of unstructured texts be facilitated by \ac{ml} techniques?]
    Unstructured texts emerge in many different domains.
    Initially, this work is motivated by the task of tax evasion detection for tax offices.
    However, this work has a broad target audience.

    \item[Which methods are scalable to large datasets?]
    The amount of information grows rapidly.
    Hence, techniques to explore information have to be scalable.
    This thesis should state obstacles and possibly limitations encountered when scaling the techniques to large datasets.

    \item[Do different embedding methods produce similar results?]
    The task at hand defines a result as a set of similar documents to a query document.
    Hence, one has to compare response sets of different methods.

    \item[Do semantic or visual embedding methods produce more meaningful embeddings?]
    The methods encode different types of information, i.e. text layer versus layout, into embeddings. 
    This thesis should explore which type of information is more meaningful for the task at hand.


\end{description}


% User Interface
In order to facilitate the exploration of the data, a \ac{ui} shall be provided.
However, this \ac{ui} is not supposed to be an operational application for end users from the tax office 
but serves the purpose of displaying the techniques examined.
It should assist the natural human approach to exploration:
A human finds a document of interest, for instance, by random sampling, and thus, wants to find similar documents.

% secondary goals
% The following bullet points are considered secondary goals which have influenced the design process of this thesis.
% \begin{description}
%     \item[Similarity of grouped documents.]
%     The document clusters should be derived from either semantically or visually similar documents.
%     \item[Topic identification.]
%     The topics identified should be meaningful to the task at hand and human interpretable.  
%     \item[Little latency.]
%     The database should be calculated offline to ensure little latency when executing queries.
%     \item[Usability.]
%     The methods should be bundled in an application, which is easy to use and does not require any programming skills.
% \end{description}